Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-07-07 Latex/sections/registration.tex
Proofread LPC section

The presented algorithm employs LPC on each individual line scan.
The idea is to find planar features utilizing an optimized approximate k nearest neighbour (AKNN) search for normal calculation as in~\cite{aknnbbs}.
Thus, normals are calculated for every point in the respective line scan.
Then, the local normal model is combined with a region growing approach.
The region growing is implemented by storing the k-nearest neighbors in a queue, which represents the iteration order of the clustering algorithm.
A region grows if one of these neighbors has a distance shorter then a treshold $d_{growth}$ and additionally has a similar normal.
The angle between two normalized vectors is
\begin{equation}
\label{eq:smallestalpha}
	\alpha(\vec{n}_1, \vec{n}_2) = \arccos(\vec{n}_1 \cdot \vec{n}_2) \; .
\end{equation}
However, the \textit{smallest} angle between two \textit{normal} vectors is 
\begin{equation}
\label{eq:alphahat}
\hat \alpha(\vec{n}_1, \vec{n}_2) = 
\begin{cases}
	2\pi - \alpha(\vec{n}_1, \vec{n}_2) & \text{if  } \alpha(\vec{n}_1, \vec{n}_2) > \frac{3}{2} \pi \\
	\alpha(\vec{n}_1, \vec{n}_2) - \pi & \text{if  } \alpha(\vec{n}_1, \vec{n}_2) > \pi \\
	\pi - \alpha(\vec{n}_1, \vec{n}_2) & \text{if  } \alpha(\vec{n}_1, \vec{n}_2) > \frac{\pi}{2} 
\end{cases}
\; ,
\end{equation}
because the opposing normals $-\vec{n}_1$ and $-\vec{n}_2$ always have to be considered, since they correspond to the same plane.
We say that two normals are similar if the angle $\hat \alpha$ from eq. \ref{eq:alphahat} is smaller than a threshold $\epsilon_{\alpha}$.

Planar areas like walls are therefore connected in one large cluster, while non-feature parts, i.e. non-planar or detached parts of the scan will have their own, smaller cluster.
You are then left with a rather easy task: filtering the clusters.
The filtering has two parts.
First, to combine clusters that are similar, i.e. have a short distance ($d_{growth}$) to each other and similar mean normals.
Second, to filter out all clusters that contain non-feature points.
Since all the non-feature points belong to small clusters, the presented algorihtm does this by putting a minimum threshold $N_{c,min}$ on the cluster size.
Figure \ref{fig:clustering} shows this concept on a real world dataset.
It was obtained by a floating sphere on a desk in an office environment, as described later in section \ref{sec:experimentalSetup}.

@@

Point-to-Plane correspondences are now established.
The distance models (Hesse + PPD) are utilized to check wether a cluster overlaps with any of the global planes, i.e. any point in the cluster has a Hesse distance smaller than some threshold $\epsilon_H$ and a PPD smaller than some additional threshold $\epsilon_P$, to the global plane.
For each overlap, we find the smallest angle between the corresponding cluster normal and the global plane normal, according to eq. \ref{eq:alphahat}.
Finally, a correspondence is established between all points in the cluster and the global plane, if the minimum angle between their normals is smaller than $\epsilon_\alpha$.

>>>>

The presented algorithm employs LPC on each individual line scan.
The idea is to find planar features utilizing an optimized approximate k nearest neighbor (AKNN) search for normal calculation as in~\cite{aknnbbs}.
Thus, normals are calculated for every point in the respective line scan.
Then, the local normal model is combined with a region growing approach.
The region growing is implemented by storing the k-nearest neighbors in a queue, which represents the iteration order of the clustering algorithm.
A region grows if one of these neighbors has a distance shorter then a threshold $d_{growth}$ and additionally has a similar normal.
We define similarity of two normals via the angle between them, which is:
\begin{equation}
\label{eq:smallestalpha}
	\alpha(\vec{n}_1, \vec{n}_2) = \arccos(\vec{n}_1 \cdot \vec{n}_2) \; .
\end{equation}
However, the \textit{smallest} angle between two \textit{normal} vectors is 
\begin{equation}
\label{eq:alphahat}
\hat \alpha(\vec{n}_1, \vec{n}_2) = 
\begin{cases}
	2\pi - \alpha(\vec{n}_1, \vec{n}_2) & \text{if  } \alpha(\vec{n}_1, \vec{n}_2) > \frac{3}{2} \pi \\
	\alpha(\vec{n}_1, \vec{n}_2) - \pi & \text{if  } \alpha(\vec{n}_1, \vec{n}_2) > \pi \\
	\pi - \alpha(\vec{n}_1, \vec{n}_2) & \text{if  } \alpha(\vec{n}_1, \vec{n}_2) > \frac{\pi}{2} 
\end{cases}
\; ,
\end{equation}
because the opposing normals $-\vec{n}_1$ and $-\vec{n}_2$ always have to be considered, since they correspond to the same plane.
We say that two normals are similar if the angle $\hat \alpha$ from eq. \ref{eq:alphahat} is smaller than a threshold $\epsilon_{\alpha}$.

Planar areas like walls are therefore connected in one large cluster, while non-feature parts, i.e. non-planar or detached parts of the scan will have their own, smaller cluster.
Finally the clusters are filtered in two steps.
First, to combine clusters that are similar, i.e. have a short distance ($d_{growth}$) to each other and similar mean normals (similarity defined as before).
Second, to filter out all clusters that contain non-feature points.
Since all the non-feature points belong to small clusters, the presented algorihtm does this by putting a minimum threshold $N_{c,min}$ on the cluster size.
Figure \ref{fig:clustering} shows this concept on the real world dataset described later in section \ref{sec:experimentalSetup}.

@@

Point-to-Plane correspondences are now established.
The distance models (Hesse and PPD) are utilized to check whether a cluster overlaps with any of the global planes, i.e. any point in the cluster has a Hesse distance smaller than some threshold $\epsilon_H$ and a PPD smaller than some additional threshold $\epsilon_P$, to the global plane.
For each overlap, we find the smallest angle between the corresponding cluster normal and the global plane normal, according to eq. \ref{eq:alphahat}.
Finally, a correspondence is established between all points in the cluster and the global plane, if the minimum angle between their normals is smaller than $\epsilon_\alpha$.
